\chapter*{Preface}\addcontentsline{toc}{chapter}{Preface}

This document started out as my notes while a student in Andrew Ng's Machine Learning course on Coursera. If this subject is of any interest to you, I highly recommend you check out the course \href{https://www.coursera.org/learn/machine-learning}{here}. \\


All credit for content contained herein goes to Andrew Ng and his course. \\

In creating these notes, there are some changes I have made to the content. Primarily, I switched from using the programming language used for the course, Octave, to Python. I believe Python is a more practical choice, and it is also my programming language of choice. Additionally, by using Python, I believe I am not violating any aspect of Coursera's honor code by posting some of my solutions to the exercises. The solutions look completely different in Python, and therefore won't really be of any help to those trying to complete the course. Whether you know Python or not, the notes on the mathematics and the course content should prove useful. I also include random tidbits of ML knowledge I've picked up from other places sporadically throughout. \\

These notes fill follow this format: each chapter will cover a week of the Coursera course. The theory that is covered in Professor Ng's videos will be the majority of these notes. The homework, coded in Python, comes next. It goes over my implementation of the methods discussed in the course. I'll include some of the homework text, but I may remove any Octave or MATLAB specifics, since they don't apply here. Finally, I'll end most sections with notes on `Python Labs,' which will be using pre-built Python modules to implement these techniques. \\

The most recent version of these notes will be kept on my GitHub page at \url{https://github.com/Sz593/coursera_ml_notes}. If you have questions or comments, you can email me at \href{mailto:simonzahn@gmail.com}{simonzahn@gmail.com}.